Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
cosmetic changes around Eq 12
\parallel -> \Vert ; \bullet -> \cdot in Eq 12
refs Bardeli and Obrist

As stated in the introduction, the field of ecoacoustics is relatively young, but significant works are worth mentioning.
One avenue of research, originated in bioacoustics, intends to retrieve the species that produced a given sonic event of relatively short duration, in order to link animal vocalization with behavior\cite{au2008principles, stowell2014large}.
A more recent paradigm processes the audio stream at hand in a holistic way, as it describes the auditory environment over larger temporal scales, without assuming that one single species is present throughout the recording. Automated systems belonging to this paradigm aim at inferring global properties of bioacoustic scenes, including biodiversity indices \vl{ref}, migration patterns \vl{ref}, as well as regions of particular interest before human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

@@

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}: \\
\begin{equation}
\label{eq:kc}
\begin{split}
K^c_{ij} & =exp\left( - \dfrac{\parallel c_i - c_j \parallel^2}{\sigma_{i}\sigma_{j}} \right) \\
\sigma_{i} & =\parallel c_i - c_N \parallel
\end{split}
\end{equation}

with $c_N$ the $N$'th nearest neihgbor of the centroid $c_i$, and $\parallel \bullet \parallel$ the euclidean norm.

>>>>

As stated in the introduction, the field of ecoacoustics is relatively young, but significant works are worth mentioning.
One avenue of research, originated in bioacoustics, intends to retrieve the species that produced a given sonic event of relatively short duration, in order to link animal vocalization with behavior\cite{au2008principles, stowell2014large}.
A more recent paradigm processes the audio stream at hand in a holistic way, as it describes the auditory environment over larger temporal scales, without assuming that one single species is present throughout the recording. Automated systems belonging to this paradigm aim at inferring global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as regions of particular interest before human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

@@

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
K^c_{ij} = exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_i - c_N \Vert}
\end{equation}

where $c_N$ is the $N^{\mathrm{th}}$ nearest neihgbor of the centroid $c_i$, and $\Vert \cdot \Vert$ denotes the Euclidean norm.
